Checkpoint 3

### 2020-04-23 Checkpoint3.Rmd

```{r}
google<-read.csv("Google/googlefinal.csv")
```

Re-Cleaned 
```{r}
Finaldata <- Finaldata %>% select(-c(X)) 
Finaldata <- Finaldata %>% mutate(as.Date(Day))
```

@@

##Visualizations 
```{r}
google %>% 
  group_by(Region, Day) %>% 
  summarize(ChinaVirusSearch = median(ChinaVirusInterest)) %>% 
  ggplot(aes(x=Day, y=ChinaVirusSearch, color=Region))+
  geom_point()
```

@@

```{r}
## Positive COVID cases map before and after week 
library(statebins)
plot3<-statebins(state_data = weekbefore, state_col = "state",
                     text_color = "white", value_col = "positive",
                     brewer_pal="Spectral", font_size = 3,breaks =7,
                     legend_title="Week Before",
                 labels = c("0","1-5","5-10","10-20","20-30","30-40","50-100"))

>>>>

```{r}
google<-read.csv("Google/googlefinal.csv")
names(google)
```

Re-Cleaned 
```{r} 
google <- google %>%  select(-c(X.1))
Finaldata <- Finaldata %>% select(-c(X)) 
Finaldata <- Finaldata %>% mutate(as.Date(Day))
```

@@

##Visualizations 
```{r}
library(plotly)
#google_ts<-read.csv("Time_series_Google.csv")

day1<-as.Date("03/10/2020",format = "%m/%d/%Y")
day2<-as.Date("03/24/2020",format = "%m/%d/%Y")

google_ts<-google%>%
  mutate(Day = as.Date(as.character(Day)))

a<-google_ts %>% 
  #filter(Day<=day2)%>%
  #filter(Day>=day1)%>%
  group_by(Region, Day) %>% 
  summarize(ChinaVirusSearch = median(ChinaVirusInterest)) %>% 
  ggplot(aes(x=Day, y=ChinaVirusSearch, color=Region))+
  geom_point()

ggplotly(a)
```

@@

```{r}
## Positive COVID cases map before and after week 
plot3<-statebins(state_data = weekbefore, state_col = "State",
                     text_color = "white", value_col = "positive",
                     brewer_pal="Spectral", font_size = 3,breaks =7,
                     legend_title="Week Before",
                 labels = c("0","1-5","5-10","10-20","20-30","30-40","50-100"))
